%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
\vspace{0pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule\vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1\vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{0pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

\begin{center}
    \textbf{\Huge {Amith Hossain}} \\ \vspace{4pt}
    \underline{amith12355@gmail.com} $|$
    \href{https://linkedin.com/in/amithhossain}{\underline{linkedin.com/in/amithhossain/}} $|$
    \underline{+353 85 162 4396}
\end{center}


%-----------SUMMARY-----------
\section{Summary}
  Experienced DevOps / Production Engineer with \textbf{7 years of proven expertise} in maintaining high availability systems and critical software development within distributed, ultra low latency environments. Skilled at designing and developing complex python \textbf{workflows}, \textbf{automations}, \textbf{monitoring} and \textbf{observability} solutions.


%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {DevOps / Production Engineer}{Oct 2023 -- Present}
      {Susquehanna International Group}{Dublin, Ireland}
      \resumeItemListStart
        \resumeItem{Proactively monitored and resolved production issues within low latency trading environment comprising \textbf{10 global regions} and \textbf{200+ bare metal hosts}. Specialized in \textbf{network} connectivity, \textbf{server} outages, and \textbf{software} crashes}
        \resumeItem{Took ownership and delivered on DevOps and infrastructure requirements to commence trading on \textbf{3 new exchanges} overcoming complex roadblocks through cross-functional collaboration.}
        \resumeItem{Streamlined software deployments using Octopus Deploy \textbf{reducing software deployment times by 15 mins}.}
        \resumeItem{Utilized \textbf{Ansible} across trading environment eliminating configuration drift and consistent deployments.}
        \resumeItem{Designed and Developed complex data pipelines and automations using Apache Airflow and Python \textbf{eliminating 4 hours of manual weekly toil}.}
        \resumeItem{Developed web dashboard in Python (Flask) enabling \textbf{observability into 250+ reconciliation workflows}.}
        \resumeItem{Developed custom API endpoint monitoring and alerting solution for a critical time sync service on \textbf{35 hosts split between Chicago and Frankfurt}.}
        \resumeItem{Planned and executed migration to .NET 8. Developed ansible playbook and installed .NET 8 across \textbf{300+ Prod and Dev hosts}. Deployed and tested new versions of \textbf{16 Trading Apps}. Collaborated with Traders to seamlessly switch over with minimal downtime}
        \resumeItem{Refactored \textbf{20+ legacy automations}, improving functionality and reliability.}
        \resumeItem{Maintained code base utilizing \textbf{version control} best practices and code reviews with asynchronous tools such as Jira, Confluence, and GitLab.}
      \resumeItemListEnd

    \resumeSubheading
      {Site Reliability Engineer}{Sep 2021 -- Oct 2023}
      {ServiceNow}{Dublin, Ireland}
      \resumeItemListStart
        \resumeItem{Carried out testing and QA of \textbf{70+ automations} for new data center rollout resolving bugs and blockers completing all requirements \textbf{3 weeks ahead of schedule}}
        \resumeItem{Took \textbf{initiative} to explore and evaluate an existing underused automation platform. \textbf{Created proof of concept} and collaborated with fellow engineers, leading to reduction in monitoring noise.}
        \resumeItem{Maintained databases and web servers which consisted of load-balancing, upgrades, performance, migrations, backups, restores and manual configuration changes following ITIL practices.}
        \resumeItem{Drove resolution of incidents and escalations related to customer ServiceNow Instances.}
    \resumeItemListEnd

    \resumeSubheading
      {Senior Technical Support Engineer}{Oct 2018 -- Sep 2021}
      {VMware}{Cork, Ireland}
      \resumeItemListStart
        \resumeItem{\textbf{Managed escalations} from Microsoft and Google engineers on their respective VMware cloud platforms.}
        \resumeItem{\textbf{Promoted twice within 3 years} to a senior position by vastly exceeding expectations set by management.}
        \resumeItem{Resolved technical issues with VMware products such as VCF, vSphere, vCenter.}
        \resumeItem{Engaged engineering teams to resolved bugs encountered and advocate for new features required by customers}
      \resumeItemListEnd

  \resumeSubHeadingListEnd


%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: Python, Go, Powershell, Bash, SQL, HTML/CSS} \\
     \textbf{Tools}{: Git, Apache Airflow, Ansible, Jira/Confluence, Octopus Deploy} \\
     \textbf{General}{: Networking, Windows, Linux, Software Development, Automations, APIs} \\
    }}
 \end{itemize}




%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Trinity College Dublin}{Dublin, Ireland}
      {BSc Electronic Engineering}{Sep 2014 -- May 2018}
  \resumeSubHeadingListEnd


%-------------------------------------------
\end{document}